---
title: "Assignment_2"
author: "Swetha"
date: "11/15/2022"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

##Integer Programming

AP is a shipping service that guarantees overnight delivery of packages in the continental US. The company has various hubs at major cities and airports across the country. Packages are received at hubs, and then shipped to intermediate hubs or to their final destination.
The manager of the AP hub in Cleveland is concerned about labor costs, and is interested in determining the most effective way to schedule workers. The hub operates seven days a week, and the number of packages it handles varies from one day to another.

Setting default values to get a clean output


```{r}
#loading the .lp file
getwd()
setwd("C:/Users/mercy/OneDrive/Desktop/QMM/Assignment_6")
```

```{r}
#Loading the lpSolveAPI Package
library("lpSolveAPI")
```


```{r}
library(tinytex)

#Loading the lp file
AP_HUB <- read.lp("IntegerProgramming.lp")
print(AP_HUB)
```

```{r}
#We are estimating the number of workers required for every day for week in the table below
Required_Workers_Daywise<- matrix(c("Sunday","Monday","Tuesday","Wednesday","Thursday","Friday","Saturday",
18,27,22,26,25,21,19),ncol=2,byrow = F)
colnames(Required_Workers_Daywise) <- c("No_of_Days_per_week", "No_of_Workers_Required")
as.table(Required_Workers_Daywise)
```

Package handlers at AP are guaranteed a five-day work week with two consecutive days off. The base wage for the handlers is $750 per week. Workers working on Saturday or Sunday receive an additional $25 per day. The possible shifts and salaries for package handlers are

```{r}
No_of_Day_offs_and_wages <- matrix(c(1,2,3,4,5,6,7, "Sunday and Monday","Monday and Tuesday","Tuesday and Wednesday","Wednesday and Thursday","Thursday and Friday","Friday and Saturday","Saturday and Sunday","$775","$800","$800","$800","$800","$775","$750"),ncol=3,byrow=F)
colnames(No_of_Day_offs_and_wages) <- c("Shifts", "Day_Offs", "Wages")
as.table(No_of_Day_offs_and_wages)
```

```{r}
#Now Running the lp model
solve(AP_HUB)
```

By getting 0 as the value we get to know that there exists a model.


```{r}
#Objective Function
get.objective(AP_HUB)
```
The overall cost to the company to ensure that total pay expenses are as little as feasible and that there are enough workers available each day to work is "25,675$".

```{r}
#The number of workers whom is available to work each day
get.variables(AP_HUB)
```
The variables have values from x1, x2.......x7 where,
x1 = Number of workers assigned to shift 1 = 2
x2 = Number of workers assigned to shift 2 = 4
x3 = Number of workers assigned to shift 3 = 5
x4 = Number of workers assigned to shift 4 = 0
x5 = Number of workers assigned to shift 5 = 8
x6 = Number of workers assigned to shift 6 = 1
x7 = Number of workers assigned to shift 7 = 13
With respect to the objective function as well as the limits set by the business, we may determine how many workers are available to work each day by the variable values obtained.
Sunday = x2 + x3 + x4 + x5 + x6 = 18 Workers
Monday = x3 + x4 + x5 + x6 + x7 = 27 Workers
Tuesday = x4 + x5 + x6 + x7 + x1 = 24 Workers
Wednesday = x5 + x6 + x7 + x1 + x2 = 28 Workers
Thursday = x6 + x7 + x1 + x2 + x3 = 25 Workers
Friday = x7 + x1 + x2 + x3 + x4 = 24 Workers
Saturday = x1 + x2 + x3 + x4 + x5 = 19 Workers