---
title: "Assignment_2"
author: "Swetha"
date: "9/20/2022"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Loading the "lpSolve","lpSolveAPI" packages.
library(lpSolve)
library(lpSolveAPI)
```
```{r}
# setting up the working directory
getwd()
setwd("C:/Users/mercy/OneDrive/Desktop/QMM/Assignment_2")
```
# From the LP problem we  have to find objective function, constraints and decision variables.
```{r}
# starting the lp problem with 12 constraints and 9 decision variables.
lprec <- make.lp(12,9)
```

```{r}
# Setting the objective function for the problem.
set.objfn(lprec, c(420,420,420,360,360,360,300,300,300))
# and Changing the direction to setup maximization
lp.control(lprec, sense = "max")
```

```{r}
# Setting up all the constraint values row by row
# Capacity constraints:
set.row(lprec, 1, c(1,1,1), indices = c(1,4,7))
set.row(lprec, 2, c(1,1,1), indices = c(2,5,8))
set.row(lprec, 3, c(1,1,1), indices = c(3,6,9))
# Storage constraints:
set.row(lprec, 4, c(20,15,12), indices = c(1,4,7))
set.row(lprec, 5, c(20,15,12), indices = c(2,5,8))
set.row(lprec, 6, c(20,15,12), indices = c(3,6,9))
# Sales constraints:
set.row(lprec, 7, c(1,1,1), indices = c(1,2,3))
set.row(lprec, 8, c(1,1,1), indices = c(4,5,6))
set.row(lprec, 9, c(1,1,1), indices = c(7,8,9))
# Capacity usage constaints:
set.row(lprec, 10, c(900,900,900,-750,-750,-750), indices = c(1,4,7,2,5,8))
set.row(lprec, 11, c(450,450,450,-900,-900,-900), indices = c(2,5,8,3,6,9))
set.row(lprec, 12, c(450,450,450,-750,-750,-750), indices = c(1,4,7,3,6,9))
```

```{r}
# Setting all the right hand side values
rhs <- c(750,900,450,13000,12000,5000,900,1200,750,0,0,0)
set.rhs(lprec, rhs)
```

```{r} 
# Set up the constraint type
set.constr.type(lprec, c("<=","<=","<=","<=","<=","<=","<=","<=","<=","=","=","="))
```

Now,For this problem all the values must be greater than 0.

```{r}
# Setting the boundary condiiton for the decision variables
set.bounds(lprec, lower = rep(0, 9))
```

```{r}
# Setting the names of the rows as constraints and the columns as decision variables.
lp.rownames <- c("Plant 1 Capacity", "Plant 2 Capacity", "Plant 3 Capacity", "Plant 1 Storage", "Plant 2 Storage", "Plant 3 Storage", "Large Sales", "Medium Sales", "Small Sales", "Plant 1 and 2 Usage", "Plant 2 and 3 Usage", "Plant 1 and 3 Usage")
lp.colnames <- c("Plant 1L", "Plant 2L", "Plant 3L", "Plant 1M", "Plant 2M", "Plant 3M", "Plant 1S", "Plant 2S", "Plant 3S")
dimnames(lprec) <- list(lp.rownames, lp.colnames)
```

Before running the code, this command should return the linear program outline so we can verify that all the values are valid.

```{r}
# Now Return the linear programming object to ensure the values are correct
lprec
# This model can also be saved to a file
write.lp(lprec, filename = "Assignment-2.lp", type = "lp")
```

This following code will now look for an optimal solution. If it returns "0" value then that means the model has found an optimal solution.

```{r}
# Solving the linear program
solve(lprec)
```

This model returned a "0", so it has found an optimal solution to the problem.The function below will return what the maximum value for the objective function will be.

```{r}
# Reviewing the objective function value
get.objective(lprec)
```
In this case, the maximum profits that can be achieved with these constraints is $696,000 per day.In order to determine how many units of each kind of product the plants should produce, we will then return the values of the decision variables.
```{r}
# Get the optimum decision variable values
get.variables(lprec)
```
The Optimum decision variable values from the model:

Plant 1, Large: 516.67 units/day
Plant 2, Large: 0 units/day
Plant 3, Large: 0 units/day
Plant 1, Medium: 177.78 units/day
Plant 2, Medium: 666.67 units/day
Plant 3, Medium: 0 units/day
Plant 1, Small: 0 units/day
Plant 2, Small: 166.67 units/day
Plant 3, Small: 416.67 units/day

The following two segments of code will tell us where our values fall within the constraints, as well as return the surplus between the constraint and the actual value from the constraints.

```{r}
# Get the constraint values for the problem
get.constraints(lprec)
```

```{r}
# Reviewing the surplus for each constraint
get.constraints(lprec) - rhs
```

The "get.sensitivity.rhs()" function will be used to identify the shadow prices for the right hand side and objective function of the formulated linear programming problem.

```{r}
get.sensitivity.rhs(lprec)
```

```{r}
get.sensitivity.obj(lprec) 
```

## Dual Problem:

```{r}
# Begining the dual lp problem with 9 constraints and 12 decision variables.
lprecdual <- make.lp(9,12)
```

```{r}
# Setting up the objective function for the problem.
set.objfn(lprecdual, c(750,900,450,13000,12000,5000,900,1200,750,0,0,0))
# Changing the direction to set minimization
lp.control(lprecdual, sense = "min")
```

```{r}
# Setting up all the constraint values row by row
set.row(lprecdual, 1, c(1,20,1,900,450), indices = c(1,4,7,10,12))
set.row(lprecdual, 2, c(1,15,1,900,450), indices = c(1,4,8,10,12))
set.row(lprecdual, 3, c(1,12,1,900,450), indices = c(1,4,9,10,12))
set.row(lprecdual, 4, c(1,20,1,-750,450), indices = c(2,5,7,10,11))
set.row(lprecdual, 5, c(1,15,1,-750,450), indices = c(2,5,8,10,11))
set.row(lprecdual, 6, c(1,12,1,-750,450), indices = c(2,5,9,10,11))
set.row(lprecdual, 7, c(1,20,1,-900,-450), indices = c(3,6,7,11,12))
set.row(lprecdual, 8, c(1,15,1,-900,-450), indices = c(3,6,8,11,12))
set.row(lprecdual, 9, c(1,12,1,-900,-450), indices = c(3,6,9,11,12))
```

```{r}
# Setting all the right hand side values
rhs2 <- c(420,420,420,360,360,360,300,300,300)
set.rhs(lprecdual, rhs2)
```

```{r}
# Now Setting the constraint type
set.constr.type(lprecdual, c(">=",">=",">=",">=",">=",">=",">=",">=",">="))
```

```{r}
# Setting up the boundary condiiton for the decision variables
set.bounds(lprecdual, lower = c(0,0,0,0,0,0,0,0,0,-1.00e+30,-1.00e+30,-1.00e+30))
```

```{r}
# Solving the linear program
solve(lprecdual)
```

```{r}
# Reviewing the objective function value
get.objective(lprecdual)
```

```{r}
# Getting the optimum decision variable values
get.variables(lprecdual)
```

```{r}
get.sensitivity.rhs(lprecdual)
```

```{r}
get.sensitivity.obj(lprecdual)
```